
\documentclass[11pt]{article}


\usepackage{a4wide}

\begin{document}

\title{Pentesting Report: Smart WiFi Camera}
\author{Haohan Fu (), Jiayang Xu (2829543), Zhengyang Cheng (),
\\ Xi Wang (), Xibin Yu () and Haoyu Ju ()}
\date{12, March, 2025}
\maketitle







\section{Executive summary}

Give the high lights of your report, what are your key results and recommendations?

\section{High-level description of the device}

What is the device and what does it do? How does it work? Does it take commands, from a phone app? A cloud server? How does the user set it up? Etc.

\section{Investigating the device}

\subsection{Analysing the device setup}

Describe the technical details of how the device is set up by the user. What protocols are used and how? How did you fine this out? Give technical details, and enough information to ensure that your analysis is repeatable by someone else.

\subsection{Analysing the device in use}

Describe the technical details of how the device is used after set up. What protocols are used and how? How did you fine this out. Give technical details, and enough information to ensure that your analysis is repeatable by someone else.

\subsection{Analysing the apk file}

If you analysed the apk file, describe the app code and what you found.

\section{Possible attacks against the device}


\subsection{Attacks by a local attacker with wi-fi access}

What attacks are possible by an attacker with access to the same wi-fi network as the device? What could and couldnÕt such an attacker do and why? Describe both the possible attacks, if any, and also describe if the device provides defense from such an attacker, and say how. 

\subsection{Attacks by a local attacker without wi-fi access}

What attacks are possible by an attacker that is within wi-fi range of the device but does not have the wi-fi password? What could and couldnÕt such an attacker do and why? Describe both the possible attacks, if any, and also describe if the device provides defense from such an attacker, and say how. 

\subsection{Attacks by a remote attacker}

What attacks are possible by a remote attackers that can intercept and send messages on the Internet? What could and couldnÕt such an attacker do and why? Describe both the possible attacks, if any, and also describe if the device provides defense from such an attacker, and say how. 

\section{Analysis of the weaknesses found}

For each of the weaknesses you have found, describe the risk they pose to the owner of the device. What is the impact of the attacks? What would your advice be to someone that owned used such a device?


 
\appendix

\section{Additional technical information}

Include additional technical information to support your report. APK files, pcap files, Burp logs, a proof of concept attack code can be given to me on a USB stick.
\end{document}

